\chapter{Bootloaders}

\section{Keith\&Koep ``arnoldboot'' (TrizepsIV)}

Three kernel image types:

\begin{description}
\item[\texttt{*-sdram.bin}]
\item[\texttt{*-flash.bin}]
\item[\texttt{*-gdb.bin}]
\end{description}

\begin{verbatim}
fuseburn 9
fuselist
\end{verbatim}



\begin{verbatim}
setbaud com1 115200

boot mmc kernel.img
boot mmc rootfs.img

tftp
\end{verbatim}

\section{Keith\&Koep ``e-boot'' (TrizepsVI)}

Four parts

\begin{description}
\item[\texttt{autoboot.bat}] To be copied into the e-boot boot
  partition. Adjust it to local requirements
\begin{lstlisting}[language=sh]
:) bfmt                     # optionally; erases previous boot partition
:) mount nanddisk
:) del autoboot.bat
:) store mmc2 autoboot.bat  # 'mmc'  ... external slot,
                            # 'mmc2' ... on-module slot
\end{lstlisting}
\item[\texttt{boot.bin}] First stage bootloader; to be copied into the first
  (*FAT) partition of the sd-card
\item[\texttt{zImage-kk-trizeps6.bin}] Flat linux kernel; to be copied
  into the first first (*FAT) partition of the sd-card and renamed to
  \texttt{linux.ram}
\item[\texttt{elito-image-kk-trizeps6.tar.bz2}] RootFS; to be
  extracted into an ext4 partition of the sd-card. Extraction must be
  done as root to set correct file ownership.
\end{description}

\section{Keith\&Koep i-PAN4 + Trizeps MX28}

\begin{enumerate}
\item Build complete set of images (normal and rescue images plus the
  resulting stream)
  \begin{lstlisting}[language=sh]
    make all-images
    make image-stream
  \end{lstlisting}
  You will get two files
  \begin{description}
  \item [\texttt{tmp/deploy/images/rescue-zimage-\$PROJECT-image.sb}]
    Freescale SB stream going to be downloaded by the
    \texttt{imx-usbdownloader} tool below
  \item [\texttt{tmp/deploy/images/\$PROJECT-image.stream}] A stream
    containing kernel, bootloader, rootfs and other data; it can be
    transmitted over TCP, HTTP or on SD Card to the rescue system
    which writes theses parts at the right places.  Integrity of the
    hunks can be guaranteed by x.509 signatures or simple hashes.
  \end{description}
\item Configure device to boot from USB
  \begin{description}
  \item[i-PAN4] Remove the SD Card
  \item[Trizeps MX28] tbd; might be not possible withouth hardware
    modifications atm (2013-04-05)
  \end{description}
\item Execute as root
  \begin{lstlisting}[language=sh]
    imx-usbdownloader -f .../tmp/deploy/images/rescue-zImage-kk-ipan4.sb
  \end{lstlisting}

  The \texttt{imx-usbdownloader} tool must be built either manually;
  see a sample
  \href{http://www.sigma-chemnitz.de/elito/sources/imx-usbdownloader-0.0.2-1.fc17x.src.rpm}{RPM}
  for reference.  Alternatively, it can be built with
  \begin{lstlisting}[language=sh]
    ./bitbake imx-usbdownloader
    ./bitbake imx-usbdownloader-native
  \end{lstlisting}
  The results of the first command are to be executed on the target
  platform; the second command requires that the \texttt{libudev}
  development files are installed on the host.
\item Turn on the target device; it will use DHCP to obtain an IP
  address so look into the logfiles of the dhcp server or dump the
  network traffic to find out the address.  Alternatively, the ip
  address will be given out on the DUART serial port (requires a
  special flat cable and ttl/rs232 adapter).
\item Transmit the image stream
  \begin{lstlisting}[language=sh]
    nc $IP 8000 < tmp/deploy/images/\$PROJECT-image.stream
  \end{lstlisting}
% $
  Progress will be printed on stdout; see
  \ref{app:log:mx28_rescue_system} for sample logs.
\item Reset the device
\end{enumerate}


\section{Toradex Bootloader (Colibri270)}

\paragraph{NOTE:} Content of this section is preliminary and consists
of extracts from e-mail communication about creation of U-Boot images.
Integration into the buildsystem is missing.  It assumes the Fedora
implementation of the tftp client program.

\subsection{Build CE tools}

\begin{enumerate}
\item Clone the git repository and go into it
\begin{lstlisting}[language=sh]
$ git clone git://git.sigma-chemnitz.de:443/pub/ce-bootme
$ cd ce-bootme
\end{lstlisting}
\item Build and install it manually
\begin{lstlisting}[language=sh]
$ make && make install
\end{lstlisting}%$
or create an rpm package
\begin{lstlisting}[language=sh]
$ make dist
$ rpmbuild -tb ce-bootme.tar.xz
\end{lstlisting}
\end{enumerate}

The RPM package adds a ``ce-'' prefix to the installed programs which
is used in the examples below. ``ce-bootme'' needs to listen on the
privileged 980/udp port so that it must be started by the ``root''
user or installed with suid permissions (which is done by the RPM
package).

\subsection{Creating .nb images}

\paragraph{NOTE:} This section describes generation of U-Boot images
which are to be loaded at address 0.

\begin{enumerate}
\item create the .nb image from the u-boot.bin image
\begin{lstlisting}[language=sh]
$ ce-data2bin u-boot.bin 0 > u-boot.nb
\end{lstlisting}%$
\end{enumerate}


\subsection{Using .nb images}

\begin{enumerate}
\item install the tftp-client package
\item execute it
\begin{lstlisting}[language=sh]
$ ce-bootme u-boot-SAx.nb COLIBRI\*
\end{lstlisting}%$

\item connect to the ffuart interface of the colibri module with 9600 baud

\item turn off the colibri module

\item press SPACE

\item turn on the colibri module; you will see

\begin{verbatim}
Toradex Bootloader 3.6 for Colibri Built Jun 24 2010

Press [SPACE] to enter Bootloader Menu



BootLoader Configuration:

C) Clear Flash Registry
X) Enter CommandPrompt Mode
D) Download image to RAM now
F) Download image to FLASH now
L) Launch existing flash resident image now
\end{verbatim}

\item press F

\item ce-bootme from step 3 will output something like
\begin{verbatim}
ID: COLIBRI0
mode set to octet
Connected to 192.168.2.126 (192.168.2.126), port 980
putting u-boot-SA0.nb to 192.168.2.126:boot.bin [octet]
Sent 145955 bytes in 6.1 seconds [190260 bit/s]
\end{verbatim}

     and the eboot bootloader

\begin{verbatim}
-EbootSendBootmeAndWaitForTftp
FLASH download [ 0x00000000 ==> 0x00023A37 ]

INFO: FlashErase: 0x00000000 to 0x0002FFFF.  Please wait: 100%
INFO: FlashWrite: 0x00000000 to 0x00023A37.  Please wait: 100%
Flash image. Resetting device...
\end{verbatim}

\end{enumerate}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
