\chapter{\label{app:dirtree}Directory trees}

\section{Main directory tree}
\label{sec:dirtree-main}

\dirtree{%
.1 /srv/elito/\DTcomment{git repository}.
.2 COLIBRI270/\DTcomment{see \autoref{sec:dirtree-project}}.
.2 COLIBRI320/.
.2 \dots{}.
.2 de.sigma-chemnitz/\DTcomment{git submodule}.
.2 org.openembedded/\DTcomment{git submodule}.
.2 workspace/.
.3 kernel.git\DTcomment{bare git repository}.
.3 u-boot.git\DTcomment{bare git repository}.
.3 Makefile.colibri270.
.3 Makefile.kernel.colibri270\DTcomment{used e.g. in \autoref{sec:project-customization_u-boot+kernel-modifications}}.
.3 \dots{}.
.2 Makefile.
.2 project.conf.
}\vspace{1em}

In detail, there is:
\begin{itemize}
\item the \texttt{/srv/elito} toplevel directory with configuration
  data and a makefile with some helper targets
\item the \texttt{org.openembedded} directory with a clone of the
  \href{http://www.openembedded.org}{OpenEmbedded} environment plus
  some ELiTo specific changes.
\item the \texttt{de.sigma-chemnitz} directory with the core ELiTo
  data
\item one or more project directories (see
  \autoref{sec:dirtree-project}) which contain the setup for your
  platform and which will hold the area where packages will be built
\item directories under \texttt{workspace/} with clones of (big)
  foreign projects which need usually local modifications. The Linux
  kernel and the U-Boot bootloader are examples of such projects.
\end{itemize}

\section{Project directories}
\label{sec:dirtree-project}

\dirtree{%
.1 /srv/elito/COLIBRI270.
.2 .tmp/.
.2 conf/.
.3 local.conf\DTcomment{autogenerated configuration}.
.3 project.conf\DTcomment{manual project configuration}.
.2 tmp/.
.3 deploy/.
.4 ipk/.
.5 all/.
.6 \dots{}.
.5 armv5te/.
.6 \dots{}.
.6 bzip2\_1.0.5-r2\_armv5te.ipk.
.6 \dots{}.
.5 \dots{}.
.4 images/.
.5 u-boot-toradex-colibri270.bin\DTcomment{U-Boot image}.
.5 uImage-toradex-colibri270.bin\DTcomment{Kernel image}.
.5 elito-image-toradex-colibri270.jffs2\DTcomment{Filesystem image}.
.5 elito-image-toradex-colibri270.tar.bz2\DTcomment{Rootfilesystem}.
.2 files/\DTcomment{overlay directory for \texttt{SRC\_URI}s}.
.2 recipes/\DTcomment{project specific recipes}.
.3 helloworld/.
.4 helloworld.bb.
.3 \dots{}.
.2 Makefile\DTcomment{autogenerated makefile}.
.2 Makefile.local\DTcomment{local makefile}.
.2 bitbake\DTcomment{autogenerated bitbake wrapper}.
.2 build-setup.
}\vspace{1em}

\section{NFS exportable sysroots}

\dirtree{%
.1 /srv/sysroots/.
.2 colibri270-evalboard/.
.3 bin/.
.3 etc/.
.3 lib/.
.3 \dots{}.
}

\section{Source cache}

\dirtree{%
.1 /srv/elito/.cache.
.2 setuptools-0.6c9-py2.6.egg.
.2 sources/.
.3 cvs/.
.3 git/.
.4 sources.redhat.com.git.binutils.git/.
.4 \dots{}.
.3 svn/.
.3 \dots{}.
.3 zlib-1.2.5.tar.bz2.
.3 zlib-1.2.5.tar.md5.
}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
